### 2014-05-14 lineage-movement.tex
.

These rates tell us precisely the rates at which a lineage will move, backwards in time.
For instance, the rate at which a lineage currently in a type A individual at location $x$
jumps to another type A individual at location $y$ is just $w_{AA}(y,x)$.
A lineage at the selected locus (with $r=0$) in a type A individual moves according to these jump rates.
If we follow a linked locus until the first time it is found in a type B individual,
it moves according to these jump rates, and at location $x$ recombines at rate
\begin{align}
    \gamma_A(x) = \sum_y w_{BA}(y,x) .
\end{align}
Suppose that we kill the lineage when it recombines onto type B.
Let $X_t$ denote the position of the lineage at time $t$ in the past,
with $X_t = \dagger$ if it has recombined onto B,
and let $f$ be test function with $f(\dagger)=0$.
If we let $M_r(y) = p(y) (1+s_A(y)) \left(1 - r (1-p(y)) \right)  N(y)$, then
\begin{align}
    \deriv{t} \E[f(X_t) \given X_0=x ] &= \sum_y w_{AA}(y,x) ( f(y)-f(x) ) - \gamma_A(x) f(x) \\
                                       &= \sum_y  M_r(y) m(y,x) ( f(y) - f(x)  ) - \gamma_A(x) f(x) .
\end{align}

@@

\paragraph{Recombination time}
Let $\tau_\dagger$ be the first time  the lineage recombines onto type B.
If $\rho$ is much smaller than the mixing time of a type A lineage,
then the time to recombination is roughly Exponential,
with mean
\begin{align}
    \E[\tau_\dagger] \approx \frac{1}{ \rho \int \pi(x) k(x) dx } .
\end{align}
The product $\pi(x) k(x)$ is:
\begin{align}
    \pi(x) k(x) = \frac{1}{Z} N(x)^2 p(x)^2 (1-p(x)) (1+s_A(x)) (1+(s_A(x)+s_B(x))/2) .
\end{align}

More generally, if we define
\begin{align}
    h(x) = \E[\tau_\dagger \given X_0 = x]
\end{align}
then $h$ solves the equation
\begin{align}
    0 = M'(x) h'(x) + \frac{1}{2} M(x) h''(x) - \rho k(x) h(x) + 1 .
\end{align}

>>>>

These rates tell us precisely the rates at which a lineage will move, backwards in time.
For instance, the rate at which a lineage currently in a type A individual at location $x$
jumps to another type A individual at location $y$ is just $w_{AA}(y,x)$.
A lineage at the selected locus (with $r=0$) in a type A individual moves according to these jump rates.
If we follow a linked locus until the first time it is found in a type B individual,
it moves according to these jump rates, and at location $x$ recombines at rate
\begin{align}
    \gamma_A(x) = \sum_y w_{BA}(y,x) .
\end{align}
Suppose that we kill the lineage when it recombines onto type B.
Let $X_t$ denote the position of the lineage at time $t$ in the past,
with $X_t = \rho$ if it has recombined onto B,
and let $f$ be test function with $f(\rho)=0$.
If we let $M_r(y) = p(y) (1+s_A(y)) \left(1 - r (1-p(y)) \right)  N(y)$, then
\begin{align}
    \deriv{t} \E[f(X_t) \given X_0=x ] &= \sum_y w_{AA}(y,x) ( f(y)-f(x) ) - \gamma_A(x) f(x) \\
                                       &= \sum_y  M_r(y) m(y,x) ( f(y) - f(x)  ) - \gamma_A(x) f(x) .
\end{align}

@@

\paragraph{Recombination time}
Let $\tau_\rho$ be the first time  the lineage recombines onto type B.
If $\rho$ is much smaller than the mixing time of a type A lineage,
then the time to recombination is roughly Exponential,
with mean
\begin{align}
    \E[\tau_\rho] \approx \frac{1}{ \rho \int \pi(x) k(x) dx } .
\end{align}
The product $\pi(x) k(x)$ is:
\begin{align}
    \pi(x) k(x) = \frac{1}{Z} N(x)^2 p(x)^2 (1-p(x)) (1+s_A(x)) (1+(s_A(x)+s_B(x))/2) .
\end{align}

More generally, if we define
\begin{align}
    h(x) = \E[\tau_\rho \given X_0 = x]
\end{align}
then $h$ solves the equation
\begin{align}
    0 = M'(x) h'(x) + \frac{1}{2} M(x) h''(x) - \rho k(x) h(x) + 1 .
\end{align}

The probability that a segment of length $r = \rho \sigma^2$ to one side of the selected locus
does not recombine across time $t$ is $\P\{\tau_\rho > t\}$.
Therefore, if $L_t$ is the length of the nonrecombined segment to one side of the selected locus
after time $t$, then
\begin{align}
    \E[ L_t \given X_0=x ] &= \sigma^2 \int_0^\infty \P\{ \tau_\rho > t \} d\rho \\
\end{align}
The appropriate thing to do is to look at $\E[L_T]$, where $T$ is the coalescence time.
